Response to reviewers

### 2025-01-23 Manuscript/Tables/results_differences8d_4.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & CO.d\_1 & CO.ses\_1 & CO.d\_2 & CO.ses\_2 & CO.d\_3 & CO.ses\_3 & CO.d\_4 & CO.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 79.64*** & 0.14 & 130.26*** & 0.16 & 105.45*** & 0.1 & 92.81*** & 0.08 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 67526.58*** & 0.04 & 173367.22*** & 0.06 & 216655.44*** & 0.06 & 150636.07*** & 0.04 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 1312.02*** & 0.3 & 6855.69*** & 0.47 & 8664.07*** & 0.32 & 8093.46*** & 0.2 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 3.79*** & 0.29 & 7.28*** & 0.44 & 6.82*** & 0.32 & 5.38*** & 0.23 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.02*** & 0.54 & 0.02*** & 0.5 & 0.01*** & 0.4 & 0.01*** & 0.3 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.21*** & 0.27 & 0.21*** & 0.28 & 0.16*** & 0.21 & 0.1*** & 0.13 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.01*** & 0.18 & 0.01*** & 0.2 & 0.01*** & 0.14 & 0.01*** & 0.11 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.6*** & 1.4 & 0.61*** & 2.07 & 0.47*** & 2.15 & 0.32*** & 2.17 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0 & 0.11 & 0** & 0.23 & 0*** & 0.37 & 0*** & 0.27 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & 0** & -0.29 & 0*** & -0.54 & 0*** & -0.34 & 0*** & -0.21 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0 & -0.03 & 0 & -0.1 & 0 & 0.05 & 0 & -0.1 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.01* & 0.24 & 0.01*** & 0.31 & 0*** & 0.25 & 0 & 0.07 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:56:30 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & CO.d\_rm1 & CO.ses\_rm1 & CO.d\_rm2 & CO.ses\_rm2 & CO.d\_rm3 & CO.ses\_rm3 & CO.d\_rm4 & CO.ses\_rm4 \\ 
  \hline
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 67526.58*** & 0.04 & 173367.22*** & 0.06 & 216655.44*** & 0.06 & 150636.07*** & 0.04 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 1312.02*** & 0.3 & 6855.69*** & 0.47 & 8664.07*** & 0.32 & 8093.46*** & 0.2 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 3.79*** & 0.29 & 7.28*** & 0.44 & 6.82*** & 0.32 & 5.38*** & 0.23 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.21*** & 0.27 & 0.21*** & 0.28 & 0.16*** & 0.21 & 0.1*** & 0.13 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.01*** & 0.18 & 0.01*** & 0.2 & 0.01*** & 0.14 & 0.01*** & 0.11 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.6*** & 1.4 & 0.61*** & 2.07 & 0.47*** & 2.15 & 0.32*** & 2.17 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & 0** & -0.29 & 0*** & -0.54 & 0*** & -0.34 & 0*** & -0.21 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0 & -0.03 & 0 & -0.1 & 0 & 0.05 & 0 & -0.1 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.01* & 0.24 & 0.01*** & 0.31 & 0*** & 0.25 & 0 & 0.07 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D).CO = CO; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differencesempirical.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllll}
  \hline
 & empirical.d\_1 & empirical.ses\_1 & empirical.d\_2 & empirical.ses\_2 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & -7.28*** & -1.53 & -4.8*** & -1.08 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & -44.19*** & -1.74 & -9.72*** & -0.37 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & -17.07*** & -2.29 & -3.07*** & -0.55 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & -6.04*** & -2.38 & -4.32*** & -1.78 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.02*** & 1.45 & -0.03*** & -1.63 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.11*** & 1.28 & -0.05*** & -0.44 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.03*** & 1.64 & -0.03*** & -1.19 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & -0.41*** & -1.91 & -0.16*** & -0.52 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0* & 0.24 & 0.01*** & 2.35 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & 0.01*** & 0.97 & 0.02*** & 1.06 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0*** & -0.72 & 0*** & 0.69 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & -0.03*** & -2.23 & -0.02*** & -0.7 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each
stressor (empirical); d = difference, s = standardised effect size. Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:56:35 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllll}
  \hline
 & empirical.d\_rm1 & empirical.ses\_rm1 & empirical.d\_rm2 & empirical.ses\_rm2 \\ 
  \hline
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & -44.19*** & -1.74 & -9.72*** & -0.37 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & -17.07*** & -2.29 & -3.07*** & -0.55 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & -6.04*** & -2.38 & -4.32*** & -1.78 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.11*** & 1.28 & -0.05*** & -0.44 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.03*** & 1.64 & -0.03*** & -1.19 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & -0.41*** & -1.91 & -0.16*** & -0.52 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & 0.01*** & 0.97 & 0.02*** & 1.06 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0*** & -0.72 & 0*** & 0.69 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & -0.03*** & -2.23 & -0.02*** & -0.7 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (empirical); d = difference, s = standardised effect size. Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_model2d.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:16:05 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & equalizing.Slope & equalizing.adj.R\verb|^|2 & facilitation.Slope & facilitation.adj.R\verb|^|2 & filtering.Slope & filtering.adj.R\verb|^|2 & competition.Slope & competition.adj.R\verb|^|2 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 0.017*** & 0.02 & -0.015** & 0.012 & 0.026*** & 0.057 & -0.001 & -0.001 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 0.014** & 0.011 & -0.016** & 0.014 & 0.024*** & 0.038 & -0.009* & 0.007 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 0.007 & 0.002 & -0.006 & 0 & 0.03*** & 0.069 & 0.004 & 0 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 0.002 & -0.001 & -0.055*** & 0.07 & 0.001 & -0.001 & -0.02*** & 0.048 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.185*** & 0.578 & 0.022** & 0.009 & 0.102*** & 0.117 & 0.022** & 0.013 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.08*** & 0.396 & 0.009. & 0.003 & 0.054*** & 0.195 & 0.008* & 0.005 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.018** & 0.009 & -0.023*** & 0.04 & 0.014* & 0.004 & -0.022*** & 0.048 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.066*** & 0.436 & -0.028*** & 0.046 & -0.009. & 0.004 & -0.022*** & 0.038 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.227*** & 0.572 & 0.044*** & 0.037 & 0.091*** & 0.155 & 0.002 & -0.001 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.09*** & 0.293 & -0.002 & -0.001 & -0.027*** & 0.043 & -0.011* & 0.008 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0.018*** & 0.049 & 0.046*** & 0.179 & 0.004 & 0 & -0.012*** & 0.02 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.09*** & 0.356 & 0.14*** & 0.28 & 0.022*** & 0.037 & -0.009* & 0.005 \\ 
   \hline
\end{tabular}
\caption{Results of the model scaled metric ~ removal level per stressor (2D)} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:48:58 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & equalizing.Slope & equalizing.adj.R\verb|^|2 & facilitation.Slope & facilitation.adj.R\verb|^|2 & filtering.Slope & filtering.adj.R\verb|^|2 & competition.Slope & competition.adj.R\verb|^|2 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 0.02*** & 0.02 & -0.02** & 0.01 & 0.03*** & 0.06 & 0 & 0 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 0.01* & 0 & -0.02*** & 0.02 & 0.02*** & 0.03 & -0.01*** & 0.01 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 0.01 & 0 & -0.01 & 0 & 0.03*** & 0.06 & 0 & 0 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 0 & 0 & -0.06*** & 0.07 & 0 & 0 & -0.02*** & 0.05 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.19*** & 0.58 & 0.02** & 0.01 & 0.1*** & 0.12 & 0.02** & 0.01 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.08*** & 0.39 & 0.01. & 0 & 0.05*** & 0.19 & 0.01. & 0 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.02* & 0.01 & -0.02*** & 0.04 & 0.01. & 0 & -0.02*** & 0.05 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.06*** & 0.39 & -0.03*** & 0.05 & -0.01* & 0.01 & -0.02*** & 0.04 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.23*** & 0.57 & 0.04*** & 0.04 & 0.09*** & 0.16 & 0 & 0 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.09*** & 0.29 & 0 & 0 & -0.03*** & 0.04 & -0.01* & 0.01 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0.02*** & 0.05 & 0.05*** & 0.18 & 0 & 0 & -0.01*** & 0.02 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.09*** & 0.36 & 0.14*** & 0.28 & 0.02*** & 0.04 & -0.01* & 0 \\ 
   \hline
\end{tabular}
\caption{Results of the model scaled metric $\sim$ removal level per stressor (2D)} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_model4d.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:16:05 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & equalizing.Slope & equalizing.adj.R\verb|^|2 & facilitation.Slope & facilitation.adj.R\verb|^|2 & filtering.Slope & filtering.adj.R\verb|^|2 & competition.Slope & competition.adj.R\verb|^|2 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 0.054*** & 0.143 & -0.009 & 0.002 & 0.032*** & 0.076 & 0.002 & 0 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 0.013* & 0.007 & -0.032*** & 0.092 & 0.015** & 0.012 & -0.002 & 0 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 0.049*** & 0.122 & 0.008 & 0.002 & 0.061*** & 0.194 & 0.018*** & 0.038 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 0.03*** & 0.135 & -0.01 & 0.002 & 0.024*** & 0.09 & 0.001 & -0.001 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.164*** & 0.539 & -0.02** & 0.012 & 0.039*** & 0.023 & -0.002 & -0.001 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.108*** & 0.535 & -0.009** & 0.009 & 0.067*** & 0.258 & 0.012*** & 0.025 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.064*** & 0.145 & -0.004 & 0.002 & 0.045*** & 0.05 & 0.005* & 0.004 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.11*** & 0.52 & -0.03*** & 0.071 & 0.034*** & 0.065 & 0.004 & 0.001 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.153*** & 0.393 & 0.059*** & 0.083 & 0.014* & 0.005 & -0.035*** & 0.048 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.118*** & 0.517 & 0.013*** & 0.018 & -0.025*** & 0.06 & -0.002 & 0 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & -0.008** & 0.009 & -0.015*** & 0.016 & -0.006 & 0.002 & -0.001 & -0.001 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.016*** & 0.037 & 0.196*** & 0.535 & 0.014*** & 0.02 & -0.001 & -0.001 \\ 
   \hline
\end{tabular}
\caption{Results of the model scaled metric ~ removal level per stressor (4D)} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:48:58 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & equalizing.Slope & equalizing.adj.R\verb|^|2 & facilitation.Slope & facilitation.adj.R\verb|^|2 & filtering.Slope & filtering.adj.R\verb|^|2 & competition.Slope & competition.adj.R\verb|^|2 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 0.05*** & 0.14 & -0.01 & 0 & 0.03*** & 0.08 & 0 & 0 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 0.01* & 0.01 & -0.03*** & 0.09 & 0.02** & 0.01 & 0 & 0 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 0.05*** & 0.12 & 0.01 & 0 & 0.06*** & 0.19 & 0.02*** & 0.04 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 0.03*** & 0.13 & -0.01 & 0 & 0.02*** & 0.09 & 0 & 0 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.16*** & 0.54 & -0.02** & 0.01 & 0.04*** & 0.02 & 0 & 0 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.11*** & 0.53 & -0.01** & 0.01 & 0.07*** & 0.26 & 0.01*** & 0.03 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.06*** & 0.15 & 0 & 0 & 0.04*** & 0.05 & 0.01* & 0 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.11*** & 0.52 & -0.03*** & 0.07 & 0.03*** & 0.06 & 0 & 0 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.15*** & 0.39 & 0.06*** & 0.08 & 0.01* & 0 & -0.03*** & 0.05 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.12*** & 0.52 & 0.01*** & 0.02 & -0.02*** & 0.06 & 0 & 0 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & -0.01** & 0.01 & -0.01*** & 0.02 & -0.01 & 0 & 0 & 0 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.02*** & 0.04 & 0.2*** & 0.53 & 0.01*** & 0.02 & 0 & 0 \\ 
   \hline
\end{tabular}
\caption{Results of the model scaled metric $\sim$ removal level per stressor (4D)} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_model8d.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:16:05 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & equalizing.Slope & equalizing.adj.R\verb|^|2 & facilitation.Slope & facilitation.adj.R\verb|^|2 & filtering.Slope & filtering.adj.R\verb|^|2 & competition.Slope & competition.adj.R\verb|^|2 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 0.039*** & 0.071 & 0.013** & 0.009 & 0.026*** & 0.051 & 0 & -0.001 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & -0.023*** & 0.041 & -0.038*** & 0.122 & -0.024*** & 0.102 & -0.008*** & 0.056 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & -0.055*** & 0.159 & -0.051*** & 0.121 & -0.034*** & 0.093 & -0.007*** & 0.015 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & -0.032*** & 0.134 & -0.118*** & 0.345 & -0.059*** & 0.185 & -0.008*** & 0.03 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.088*** & 0.157 & -0.02** & 0.01 & 0.013 & 0.002 & -0.012. & 0.004 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.05*** & 0.166 & -0.022*** & 0.055 & 0.01. & 0.003 & -0.005 & 0.002 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.035*** & 0.035 & -0.004 & 0.001 & 0.028*** & 0.029 & -0.007** & 0.009 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.037*** & 0.121 & -0.029*** & 0.101 & -0.005 & 0 & -0.017*** & 0.041 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.03*** & 0.019 & 0.08*** & 0.131 & 0.041*** & 0.028 & -0.041*** & 0.05 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.077*** & 0.265 & 0.031*** & 0.09 & -0.009* & 0.006 & 0.002 & -0.001 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & -0.019** & 0.013 & -0.023*** & 0.017 & -0.02*** & 0.018 & 0.002 & -0.001 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.014** & 0.012 & 0.175*** & 0.574 & 0.08*** & 0.112 & -0.002 & -0.001 \\ 
   \hline
\end{tabular}
\caption{Results of the model scaled metric ~ removal level per stressor (8D)} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:48:58 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & equalizing.Slope & equalizing.adj.R\verb|^|2 & facilitation.Slope & facilitation.adj.R\verb|^|2 & filtering.Slope & filtering.adj.R\verb|^|2 & competition.Slope & competition.adj.R\verb|^|2 \\ 
  \hline
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & -0.02*** & 0.04 & -0.04*** & 0.12 & -0.02*** & 0.1 & -0.01*** & 0.06 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & -0.06*** & 0.16 & -0.05*** & 0.12 & -0.03*** & 0.09 & -0.01*** & 0.02 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & -0.03*** & 0.13 & -0.12*** & 0.35 & -0.06*** & 0.18 & -0.01*** & 0.03 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.05*** & 0.17 & -0.02*** & 0.06 & 0.01. & 0 & 0 & 0 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.03*** & 0.03 & 0 & 0 & 0.03*** & 0.03 & -0.01** & 0.01 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.04*** & 0.12 & -0.03*** & 0.1 & -0.01 & 0 & -0.02*** & 0.04 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.08*** & 0.26 & 0.03*** & 0.09 & -0.01* & 0.01 & 0 & 0 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & -0.02** & 0.01 & -0.02*** & 0.02 & -0.02*** & 0.02 & 0 & 0 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.01** & 0.01 & 0.17*** & 0.57 & 0.08*** & 0.11 & 0 & 0 \\ 
   \hline
\end{tabular}
\caption{Results of the model scaled metric $\sim$ removal level per stressor (8D)} 
\end{table}
